Appendix for: "Bad Forecast, Good Decision

### 2021-03-12 manuscript/appendix_B.Rmd
new run cached

n_models <- 32
rs <- seq(0.4, 2, length.out = n_models)
Ks <- seq(8, 10*8/5, length.out = n_models)
sigmas <- seq(0.05, 1.5*0.05, length.out = n_models)
pars <- data.frame(r = rs, K = Ks, sigma = sigmas)

@@

  d %>% pivot_longer(names(model_set[-1]), "model") %>%
  ggplot(aes(state, value, col=as.numeric(model))) +
  geom_hline(aes(yintercept = 0), lwd=1) + 
  geom_point(alpha = .5) + 
  geom_line(aes(state, true), col = "red") +
  coord_cartesian(ylim = c(-5, 8), xlim = c(0,16)) +
  ylab(bquote(f(x) - x)) + xlab("x") + viridis::scale_color_viridis()
```

We can easily plot the optimal policy derived from each model, as shown
in Fig3b.

```{r plot_policies}
fig3b <- policies %>%
  ggplot(aes(states, escapement, col=model, lty=model)) + 
  geom_line(lwd=2) + xlab("state")
```

@@

am1 <- adaptive_management(transitions[-1], 
                           reward, 
                           discount, 
                           x0 = x0, 
                           Tmax = 50, 
                           true_transition = transitions[[true_model]], 
                           epsilon = 0.001, 
                           max_iter = 2000)
```

```{r}
am <- am1$df %>% mutate(belief = am1$posterior[,1])
am %>%  ggplot(aes(time, states[state], col = belief)) + 
  geom_line() + 
  geom_point() +
  scale_colour_gradient(limits = c(0,1), low = pal[1], high = pal[4])
```

```{r}

am_npv <- sum(am$value * discount ^ am$time)
am_npv / npv[[1,"npv"]]
```

```{r include = FALSE}
as_tibble(am1$posterior) %>% 
  mutate(time = seq_along(V1)) %>%
  select(time = time, "1" = V1, "2" = V2) %>% 
  pivot_longer(c("1", "2"), values_to="belief", names_to = "model") %>%
  filter(time < 20) %>%
  ggplot(aes(time, belief, col=model)) + geom_line(col = pal[4])
```

>>>>

n_models <- 20
rs <- seq(0.1, 2, length.out = n_models)
Ks <- seq(1, 10*8/5, length.out = n_models)
sigmas <- seq(0.05, 1.5*0.05, length.out = n_models)
pars <- data.frame(r = rs, K = Ks, sigma = sigmas)

@@

d  %>%
  pivot_longer(names(model_set[-1]), "model") %>%
  mutate(model = as.numeric(model)) %>%
  ggplot(aes(state, value, col = model, group=model)) +
  geom_hline(aes(yintercept = 0), lwd=1) + 
  geom_line(alpha = .8) + 
  geom_line(aes(state, true), col = "red") +
  coord_cartesian(ylim = c(-5, 8), xlim = c(0,16)) +
  ylab(bquote(f(x) - x)) + xlab("x") + viridis::scale_color_viridis()
```

@@

am_many <- adaptive_management(transitions[-1], 
                           reward, 
                           discount, 
                           x0 = x0, 
                           Tmax = 20, 
                           true_transition = transitions[[true_model]], 
                           epsilon = 0.001, 
                           max_iter = 2000)
```

```{r}
i <- 1:20
posteriors <- data.frame(r = rs, K = Ks, t(am_many$posterior[i,])) %>%
  pivot_longer(starts_with("X"), 
               values_to = "probability",
               names_to = "time") %>% 
  mutate(time = as.integer(as.factor(time))) %>%
  pivot_longer(c("r", "K"), names_to="parameter")

posteriors %>%
  ggplot(aes(value, probability, group=time, col=time)) +
  geom_line(show.legend = FALSE) +
  facet_grid(~parameter, scales="free")
```

```{r}
best_model <- which.max(am_many$posterior[20,])
```

```{r, fig.cap = ""}
am_many$df %>% 
  mutate(belief = am_many$posterior[,best_model]) %>%
  ggplot(aes(time, states[state], col = belief)) + 
  geom_line() + 
  geom_point() +
  scale_colour_gradient(limits = c(0,1), low = pal[1], high = pal[4]) + 
  xlab("fish stock")
```

```{r}
am_npv <- sum(am_many$value * discount ^ am$time)
am_npv / npv[[1,"npv"]]
```

```{r include = FALSE}
as_tibble(am1$posterior) %>% 
  mutate(time = seq_along(V1)) %>%
  select(time = time, "1" = V1, "2" = V2) %>% 
  pivot_longer(c("1", "2"), values_to="belief", names_to = "model") %>%
  ggplot(aes(time, belief, col=model)) + geom_line(col = pal[4])
```
